Nodal Discontinuous Galerkin Method for the Euler Equations with Curvilinear Coordinates and Nuclear Equation of State for Astrophysics Simulations

### 2016-08-25 Documents/Euler/dgEulerCurvilinear.tex
Reworked flux jacobian for nuclear equation of state.

Here we list eigenvalues and eigenvectors of the extended Euler equations in Eq.~\eqref{eq:extendedEulerCompact}.  
Let $\bU=(\rho,u,v,w,E,n)^{T}$ and 
\begin{align}
  \bF^{1}(\bU)
  &=\big(\,u,\,u^{2}/\rho+p,\,u\,v/\rho,\,u\,w/\rho,\,(E+p)\,u/\rho,\,n\,u/\rho\,\big)^{T}, \\
  \bF^{2}(\bU)
  &=, \\
  \bF^{3}(\bU)
  &=.
\end{align}
The flux Jacobian matrices are given by
\begin{align}
  \pderiv{\bF^{1}(\bU)}{\bU}
  =
  \left(
  \begin{array}{cccccc}
  0 & 1 & 0 & 0 & 0 & 0 \\
  -(u/\rho)^{2}+c_{s}^{2} & 2\,u/\rho & 0 & 0 & p_{E} & p_{n} \\
  - u\,v/\rho^{2} & v/\rho & u/\rho & 0 & 0 & 0 \\
  - u\,w/\rho^{2} & w/\rho & 0 & u/\rho & 0 & 0 \\
  (c_{s}^{2}-h)\,u/\rho & h & 0 & 0 & (1+p_{E})\,u/\rho & p_{n}\,u/\rho \\
  -n\,u/\rho^{2} & n/\rho & 0 & 0 & 0 & u/\rho
  \end{array}
  \right),
\end{align}
where we have defined $c_{s}^{2}=\Gamma\,p/\rho$, $\Gamma=(\partial\ln p/\partial\ln \rho)$, $h=(E+p)/\rho$, $p_{E}=(\partial p/\partial E)$, and $p_{n}=(\partial p/\partial n)$

>>>>

Here we list eigenvalues and eigenvectors of the extended Euler equations in Eq.~\eqref{eq:extendedEulerCompact}.  
Let the vector of conserved variables be $\bU=(\rho,m_{1},m_{2},m_{3},E,n)^{T}$ and the flux vectors
\begin{align}
  \bF^{1}(\bU)
  &=\big(\,m_{1},\,m_{1}^{2}/\rho+p,\,m_{1}m_{2}/\rho,\,m_{1}\,m_{3}/\rho,\,(E+p)\,m_{1}/\rho,\,n\,m_{1}/\rho\,\big)^{T}, \\
  \bF^{2}(\bU)
  &=, \\
  \bF^{3}(\bU)
  &=.
\end{align}
The vector of primitive variables is $\bP=(\rho,v_{1},v_{2},v_{3},e,n)^{T}$.  
We have $v_{i}=m_{i}/\rho$ ($i=1,2,3$) and $e=E-\f{m^{2}}{2\,\rho}$, where $m^{2}=m_{1}^{2}+m_{2}^{2}+m_{3}^{2}$.  
The pressure is a function of the primitive variables $\rho$, $e$, and $n$; $p=p(\rho,e,n)$

The flux Jacobian matrices are given by
\begin{align}
  \pderiv{\bF^{1}(\bU)}{\bU}
  =
  \left(
  \begin{array}{cccccc}
  0 & 1 & 0 & 0 & 0 & 0 \\
  \big(\,p_{\rho}+\f{1}{2}p_{e}v^{2}\,\big)-v_{1}^{2} & \big(\,2-p_{e}\,\big)\,v_{1} & -p_{e}\,v_{2} & -p_{e}\,v_{3} & p_{e} & p_{n} \\
  - v_{1}v_{2} & v_{2} & v_{3} & 0 & 0 & 0 \\
  - v_{1}v_{3} & v_{3} & 0 & v_{1} & 0 & 0 \\
  \big[\big(p_{\rho}+\f{1}{2}p_{e}v^{2}\big)-H\big]\,v_{1} & H-p_{e}v_{1}^{2} & -p_{e}v_{1}v_{2} & -p_{e}v_{1}v_{3} & (1+p_{e})\,v_{1} & p_{n}\,v_{1} \\
  -n\,v_{1}/\rho & n/\rho & 0 & 0 & 0 & v_{1}
  \end{array}
  \right),
\end{align}
where $v^{2}=v_{1}^{2}+v_{2}^{2}+v_{3}^{2}$, $H=(E+p)/\rho$, $p_{\rho}=(\partial p/\partial \rho)$, $p_{e}=(\partial p/\partial e)$, and $p_{n}=(\partial p/\partial n)$.
